Towards End-user Web Scraping For Customization

### 2021-02-15 paper.tex
fix a couple typos

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites and we provide
  example usage scenarios that showcase each of our design principles.
  Our ultimate goal is to empower end-users to customize websites in an
  intuitive and flexible way, and thus make websites more malleable for
  all of its users.
\end{abstract}

@@

Live programming is implemented by continually running the
generalization algorithm on the DOM element under the user's cursor,
reverting if the user hovers away and committing when the user clicks.
The generated row and column selectors are used to highlight all the
matching elements on the website and create an adapter. Highlighting all
the matching column elements on the website provides visual feedback
about the system's generalization to the user. Creating an adapter
enables the system to populate the table view and set up the
bidirectional synchronization. Because the table is populated and the
bidirectional synchronization is set up, users can customize as they
scrape. Live programming is possible in our system because the
generalization algorithm and adapters execute very quickly. We are yet
to benchmark the performance and compare it to other
programming-by-demonstration systems like FlashExtract \citep{le2014}
that that provide live feedback.

@@

\hypertarget{generalization-algorithm}{%
\subsection{Generalization Algorithm}\label{generalization-algorithm}}

@@

\hypertarget{data-loaded-after-initial-render}{%
\subsection{Data Loaded After Initial
Render}\label{data-loaded-after-initial-render}}

>>>>

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites and we provide
  example usage scenarios that showcase each of our design principles.
  Our ultimate goal is to empower end-users to customize websites in an
  intuitive and flexible way, making the web more malleable for all of
  its users.
\end{abstract}

@@

Live programming is implemented by continually running the
generalization algorithm on the DOM element under the user's cursor,
reverting if the user hovers away and committing when the user clicks.
The generated row and column selectors are used to highlight all the
matching elements on the website and create an adapter. Highlighting all
the matching column elements on the website provides visual feedback
about the system's generalization to the user. Creating an adapter
enables the system to populate the table view and set up the
bidirectional synchronization. Because the table is populated and the
bidirectional synchronization is set up, users can customize as they
scrape. Live programming is possible in our system because the
generalization algorithm and adapters execute very quickly. We have yet
to benchmark the performance in detail and compare it to other
programming-by-demonstration systems like FlashExtract \citep{le2014}
that provide live feedback.

@@

\hypertarget{generalization-algorithm}{%
\subsubsection{Generalization
Algorithm}\label{generalization-algorithm}}

@@

\hypertarget{data-loaded-after-initial-render}{%
\subsubsection{Data Loaded After Initial
Render}\label{data-loaded-after-initial-render}}
